---
title: "JSON"
author: "Ayman Ighwair"
date: "10/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(dplyr)
library(readr)
library(haven)
library(readxl)
library(rjson)
library(jsonlite)

```

# Introduction

## What is JSON ?
JSON is short for JavaScript Object Notation, and is a popular format for storing and exchanging data on the web. It's known for its simplicity for humans to read and write and for machines to parse and generate

## What makes up the JSON language?
Every JSON  contains a key and a value. . Together they make a key/value pair.  
*   (list) Key: A key is always a string enclosed in quotation marks.
*    (list)Value: A value can be a string, number, boolean expression, array, or object.

## Importance of JSON
JSON is ideal for storing temporary data
JSON must be stored in text fomat. An advantage of this is that it can be used as a data format for any programming language, providing a high level of interoperability. This also means data stored in JSON files are easily sent between servers.  

#Reading in JSON files

## I used the jsonlite package as it takes care of different json delimeters and simplifies the process of reading in the data 





```{r}
o<-read_

```


