---
title: "JSON"
author: "Ayman Ighwair"
date: "10/14/2019"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
library(dplyr)
library(readr)
library(haven)
library(readxl)
library(rjson)
library(jsonlite)

```

# Introduction

## What is JSON ?
JSON is short for JavaScript Object Notation, and is a popular format for storing and exchanging data on the web. It's known for its simplicity for humans to read and write and for machines to parse and generate

## What makes up the JSON language?
Every JSON  contains a key and a value. . Together they make a key/value pair.  
* Key: A key is always a string enclosed in quotation marks.
* Value: A value can be a string, number, boolean expression, array, or object.

## Importance of JSON
JSON is ideal for storing temporary data
JSON must be stored in text fomat. An advantage of this is that it can be used as a data format for any programming language, providing a high level of interoperability. This also means data stored in JSON files are easily sent between servers.  

##Reading in JSON files

I used the jsonlite package as it takes care of different json delimeters and simplifies the process of reading in the data 



# About the Data 

## Intro 

Gathered from the New York Times API for Hardcover Fiction best sellers from June 7, 2008 to July 22, 2018. This dataset provides a summary of several best-selling fiction books. 

## Variables 
* Author 
* title 
* publisher
* rank 
* price

```{r,warning=FALSE, message=FALSE, include=FALSE}
#Read in the data 
yelp <- stream_in(file("C:/Users/Ighwair/Desktop/new-york-times-hardcover-fiction-best-sellers/nyt22.json"))
yelp_flat <- flatten(yelp)
yelp_tbl <- as_data_frame(yelp_flat)


```

Below is the average price of NYT best selling fiction books :

```{r,warning=FALSE,message=FALSE}
mn <- as.numeric(yelp_tbl$`price.$numberDouble`)

Average <- function(vector) {
  mean <- mean(vector, na.rm=TRUE)
  stdev <- sd(vector, na.rm=TRUE)
  return(list( mean = mean, sd = stdev))
}

Average(mn)

```

Also, a newly created column calculting the difference in ranks that happened in a week:
```{r,warning=FALSE,message=FALSE}
book<-yelp_tbl %>% select(author,title,publisher,`price.$numberDouble`,`rank.$numberInt`,`rank_last_week.$numberInt`) %>% arrange(`rank.$numberInt`)

gy<-book %>% mutate(week_rank_diff = as.numeric(`rank_last_week.$numberInt`)- as.numeric(`rank.$numberInt`)) %>% select(author,title,week_rank_diff)
gy

```


The Top 10 publishers : 

```{r,warning=FALSE,message=FALSE}

top_10 <-book %>% count(publisher) %>%  arrange(desc(n)) %>% top_n(10)
kable(top_10)

```


Below is a scatter plot to find if theres any correlation between Price and book rank : 

```{r,warning=FALSE,message=FALSE}

price <- as.numeric(yelp_tbl$`price.$numberDouble`)
a<-as.numeric(yelp_tbl$`rank_last_week.$numberInt`)
b<- as.numeric(yelp_tbl$`rank.$numberInt`)
sctr<- data.frame(price,b)
sctr<-na.omit(sctr) 
g<-ggplot(sctr,aes(x= price ,y=b))
g + geom_point() + geom_smooth(colour="red") +xlab("Price") 

```


Count of the different ranks
```{r,warning=FALSE,message=FALSE}
book<-yelp_tbl %>% select(author,title,publisher,`price.$numberDouble`,`rank.$numberInt`,`rank_last_week.$numberInt`) %>% arrange(`rank.$numberInt`)

g<-ggplot(book,aes(x= `rank.$numberInt`))
g + geom_bar() + xlab("Ranks")

```
